Galaxy Clustering Constraints on the Galaxy Size--Halo Connection

### 2017-08-31 paper/galsize_paper.tex
Changed title
Added outline of Results section

\title[The Galaxy Size--Halo Connection]
{On the Galaxy Size--Halo Connection}

@@

\begin{eqnarray}
\rhalfbulge &=& \abulge\rvir^{\alphabulge} \\
\rhalfdisk &=& \adisk\rvir^{\alphadisk} 
\end{eqnarray}

@@

>>>>

\title[The Galaxy Size--Halo Connection]
{Galaxy Clustering Constraints on the Galaxy Size--Halo Connection}

@@

\begin{eqnarray}
\label{eq:fiducial_model}
\rhalfbulge &=& \abulge\rvir^{\alphabulge} \\
\rhalfdisk &=& \adisk\rvir^{\alphadisk} 
\end{eqnarray}

@@

In \S~\ref{subsec:tests1} we show comparisons between the fiducial galaxy profile model described in \S~\ref{sec:model} and our SDSS sample. We demonstrate the sensitivity of galaxy clustering measurements to the post-infall evolution of satellite profiles in \S~\ref{subsec:tests2}, establishing the success of our fiducial model as non-trivial. In \S~\ref{subsec:tests3} we show that even highly idealized measurements of galaxy clustering and lensing are insensitive to assumptions about the relation between $\halospin$ and $\rhalf.$

\subsection{Tests of the Fiducial Power Law Model}
\label{subsec:tests1}

\subsection{Sensitivity of Clustering to Satellite Profile Evolution}
\label{subsec:tests2}

\subsection{Insensitivity of Clustering and Lensing to Halo Spin Correlations}
\label{subsec:tests3}
